Automated Topic Naming

### 2012-04-08 ese/ese.tex
minor detailed response

\subsection{Future Work}
There are several avenues of further investigation.  
More external validation would be useful. 
Although we validated our comparisons using a mailing list for each project, interviews with developers would provide more detail. 
We also think multi-label learning techniques, although in their infancy, are crucial in understanding cross-cutting concerns such as NFRs. 
We want to leverage different kinds of artifacts to discover threads of NFR-related discussions that occur between multiple kinds of artifacts.
Finally, we would like to extend this analysis to other domains, to
see what patterns might occur within those domains, such as consumer-facing software products.

>>>>

\subsection{Future Work}
There are several avenues of further investigation.  
More external validation would be useful. 
Although we validated our comparisons using a mailing list for each project, interviews with developers would provide more detail. 
We also think multi-label learning techniques, although in their infancy, are crucial in understanding cross-cutting concerns such as NFRs. 
We want to leverage different kinds of artifacts to discover threads of NFR-related discussions that occur between multiple kinds of artifacts.
Finally, we would like to extend this analysis to many other domains of
software projects, such as smart-phone apps, web-browsers, office-productivity tools, and web-services,
to see what patterns might occur within those domains. These software
project domains might share different architectural patterns and
domain concepts relevant to NFRs that could be missing from our word-lists.
